\section[Monolithic]{Monolithic}
A monolithic application is where all the logical components of the application is deployed as one unit,
which also means that it will be run in one process. For example, a standalone Python Flask application deployed to a server represents a monolithic backend system.
The frontend user interface may be served separately (e.g., from a static hosting service or a dedicated frontend server),
yet the backend can still be considered monolithic as long as its internal components are not independently deployable services.
There are multiple reasons to build a project with the monolithic architecture.

One of the benefits of the monolithic architecture is its simplicity. Since a typical monolithic application has a single codebase, it is easier for
the developers and collaborators to understand the overall structure. Even when a developer joins in the middle of the development process or
reading an older code base, understanding program will be generally easier compared to distributed systems structure. Another advantage of using the monolithic
structure is the cost. Since only one unit has to be deployed, which is simple and requires less infrastructure, it is cheaper to operate overall.
Because of the cheap cost, developers are able to experiment and deliver systems faster, which is beneficial in a fast pace environment.
Reliability is another aspect, where monolithic applications make few or no network calls, which usually means more reliable application.
Lastly, it is easier to find bugs compared to distributed systems since all the code is in one place.

On the other hand, there are also disadvantages of using the monolithic architecture. As the monolithic application grows, the application becomes harder to scale.
If different domains require different technology stacks, a monolithic architecture makes this difficult to achieve. Because all components are part of a single codebase and deployment unit,
they must typically use the same language, framework, and runtime environment. Trying to mix multiple technologies within one application can introduce dependency conflicts
and significantly increase system complexity.
Reliability is another disadvantage of the monolithic architecture.
A single bug or error occurred in the application could degrade the service and affect the whole application.
Lastly, when deploying the application, implementing any change will require redeploying the whole application, which could introduce a lot of risk of having reduced uptime of the application \cite{Gandhi_Richards_Ford_2024}.

\subsection[Layered Architecture]{Layered Architecture}

Layered architecture is a sub category of the Monolithic architecture. Applications that are designed with this architecture have three layered parts:
the presentation layer, the workflow layer, the persistence layer, and the database layer. Each layer has its own tasks and separated within one application.

\begin{itemize}
  \item \textbf{Presentation Layer:} The presentation layer is where the user interface (UI) is displayed and where the users interact with the system. All components that are related to the UI are included in this layer.
  
  \item \textbf{Workflow Layer:} The workflow layer consists of all code related to logic, such as business logic, workflows, and validations. This is where most of the application's code is contained.
  
  \item \textbf{Persistence Layer:} The persistence layer encapsulates the behavior required to make objects persistent, such as mapping the architecture or code-base hierarchies into set-based relational databases.
  
  \item \textbf{Database Layer:} The database layer is optional. This layer includes the database or any mechanism used to persist information.
\end{itemize}


Each layer may contain multiple problem domains. Let's take an application for a restaurant as an example. There could be domains such as place order,
deliver order, manage recipes, or mange inventory. Different problem domains could exist together in each layer of the application.

An implication of the layered monolithic architecture is the MVC design pattern, which is an abbreviation for model view and the controller.
In MVC, the model represents business logic and entities in the application; the view represents the user interface;
and the controller handles the workflow, stitching model elements together to provide the application’s functionality.
% (head first software architecture chapter 6)

The layered architecture has several advantages. One of them is feasibility, referring to the ease with which the system can be designed, implemented, and understood.
Since the structure is organized into distinct layers
with specific responsibilities, it is clear for developers to understand the overall structure of the code. This separation also allows technical partitioning, which makes it
much easier to manage and maintain big projects. 
Furthermore, the layered architecture is quick to build particularly among the projects that have clear relationships among the components, as different development teams can work on different layers in parallel.

There are also disadvantages to consider. The layered design could add complexity to the application compared to a simple monolithic application. 
Building a large application using the layered monolithic architecture could end up in a confusing relationship between layers and result in challenges maintaining and scale the application.
For example, if the Local Cuisine application were to be implemented in the layered architecture, the controller layer might begin
handling caching logic or directly querying the database instead of delegating responsibilities to the service and repository layers.
This kind of design change can confuse layer boundaries and increase coupling, making the system harder to maintain as it grows.
However, this would still be less complicated compared to the complexity of distributed systems discussed in section \ref{sec:distributed_systems}.
Isolation of testing is another problem since most layers are dependent on each other, testing a specific layer requires mock data or simulation of
the related layers, which could decrease the quality of the testing.

Applications that adopt a layered architecture do not always follow the exact structure from the original presentation, workflow, persistence, and database layer.
Some layers might be separated and reorganized differently.
For example, the presentation layer may be deployed independently from the rest of the application,
while other layers remain combined. Each variation introduces its own advantages and trade-offs within the layered architecture.

\subsection[Modular Monolith]{Modular Monolith}
Modular monolith is when an application is divided into different modules within the monolithic system. A module is one domain of the application,
and each domain will have its independent code base. For instance, an application for a restaurant might have different domains such as orders, deliveries, or recipes.
In this case, there could be separate databases for each module, or multiple schemas within a single database.
It is important to note that in a modular monolith, only the internal code organization is separated into modules.
Although the structure promotes logical independence, the application still follows the monolithic architectural model,
meaning it is compiled as a single unit and executed within one process.

One of the benefits of using the modular monolithic structure is the domain partitioning. Similar to the layered architecture,
separate development teams that specialize in one or more of these domains, which increases the efficiency of the work.
Similar to other monolithic applications, the performance of the application will be fast since there are no network calls within the application.
Furthermore, since all modules are separated from each other, it is easier to maintain the code.

However, code could be hard to reuse since each module have its own code. The logic and utilities could be tightly coupled to each domain,
decreasing the flexibility to reuse the code across modules compared to other monolithic structures \cite{Gandhi_Richards_Ford_2024}. Also, similar to other modular monolithic architecture
applications, as the applications grows, the logics and the databases could become complicated since all the code base is in one single application.


% Cons:
% -	Hard to reuse: Since each module have its own code, it is hard to reuse the logic and utilities across the modules
% -	Single set of architecture: Since all the code is within one application, logics and databases could become complicated, making it hard to scale.

% \subsection[Microkernal Architecture]{Microkernal Architecture}
% The microkernel architecture is consisted with a core of the application, and plugins.
% The core of the application is where the main application is being run, and the plugins are connected to the core application.
% It is used when a lot of customization is needed for the software

% There are multiple design choices that could be made within the monolithic architecture. Each structure has its
% own advantages and disadvantages, so it is important to choose the suitable structure in every situation.