%!TEX root = ../main.tex
\chapter{Introduction}\label{intro}

My first web application was a Flask application with a simple backend, frontend, a database connected to it, and a few API calls.
I thought that web development was simpler than it sounds. However, I changed my mind within a few months of learning 
the frontend and the backend side of web applications.
As I worked on projects, new problems arose as I try to make the scale of the project larger.
Also, depending on the project, I had to learn new strategies and technologies to achieve the goal I wanted.
More things were there to learn, and I started realizing that several design choices could be made in every situation.
Not being able to answer “why this specific choice?” for some of the choices I made realized that I do not have a full understanding of the decisions that could be made in web development, and led me to research this topic. 

Covering all the topics in web development was the primary goal, but it could be a lot to process a deep understanding in one year of the Independent Study period. I narrowed down my subjects to target the topics I encountered the most and personal interests, with the help of the backend roadmap \cite{Ahmed_2025}. Software architecture choices were a personal choice of interest. Although most of my applications were monolithic due to a smaller scale, I wanted to dig deeper into the structures of monolithic applications and also distributed systems, so that I could apply the knowledge when I start to work with larger-scale applications.

The second topic is database systems. I have taken the database class during my sophomore year, but web development required much deeper knowledge. Types of databases to choose, ways to structure the database for performance and scalability were always a confusion for me. To fully understand the decisions I am making, I researched this topic to be able to make logical decisions in the future when creating applications.

The last topic is about caching systems.
There were multiple times in my past projects where the application was slow due to database queries or functions to fetch data from external APIs.
Caching is one of the solutions to solve this problem, and it will be discussed throughout this project.
Caching data that calls database queries or API calls often makes the application significantly faster, 
and I want to investigate which strategies and types of caching systems are sufficient in every scenario. 

A web application that uses these three technologies is the best way to show that I have a full understanding of the choices I have made.
I developed a local cuisine recommender web application to show the knowledge and research done in these areas.
The motivation for creating an application in this domain arises from the discomfort of finding local cuisines when traveling to foreign countries.
It is a good experience to try out the local cuisines of the destination area, especially for people who love food.
However, searching directly on Google Maps does not accurately show the famous dishes in the specific region,
but rather recommends restaurants. Going straight to the restaurants sometimes works,
but sometimes it is helpful if there is a set of cuisines to try, already layout and choose the restaurant where the cuisines are available.
This needs a two-step search: first on a search engine such as Google to find the famous food in the area, and second, searching the name of the dish on Google Maps. The purpose of the Local Cuisine application is to make the process of searching restaurants more efficient.

This research article will be written in the following structure: Chapters 2, 3, and 4 will investigate the theories of topics that I have chosen, 
which will include backend software design and architecture, database systems, and caching systems, respectively. Each chapter of the theory will thoroughly research the 
design choices that could be made within each topic and how to make decisions based on each situation. Chapter 5 will discuss how the local cuisine web application
is implemented, the design choices that are made are based on the theory introduced in the previous chapters. The outcome and explanation of the final software will be addressed in 
chapter 6, including snapshots and images of the web application. Finally, the research article will conclude with the challenges throughout the whole research project and the lessons learned
in chapter 7. 



% So why would you want to use \lt instead of Microsoft Word\texttrademark? I can think of several reasons. The main one for this author is that \lt takes care of all the numbering automatically. This means that if you decide to rearrange material in your IS, you do not have to worry about renumbering or references. This makes it very easy to play around with the structure of your thesis. The second reason is that it is ultimately faster than Word\texttrademark. How? Well, after a week or so of using \lt, you will begin to remember the commands that you use frequently and won't have to use the \lt pallet in TeXShop or TeXworks. So, you can just type everything including the mathematics, where with \msw you would have to use the Equation Editor.

% I have also tried to make things more efficient by organizing the example folder as follows. There is a \texttt{main.tex} file which is what you will enter all the information about your IS into and is the document you will typeset. \texttt{main.tex} also has explanations about other files that you might need to edit. In addition, there are folders for chapters, appendices, styles, and figures. This structure is there to try and reduce file clutter and to help you stay organized. There should also be a .bib file which you can use as a model for your own .bib file. The .bib file has your bibliographic information.

% \lt is easy to learn. For an average IS, the author will only need to learn a handful of commands. For this small bit of effort, you get a tremendous amount of flexibility and a very beautiful document. The following chapters will introduce some of the common things a student might need to do in a thesis.

% \section{What is in \texttt{main.tex}?}
% Before we move on let's talk a little bit about what is at the beginning of \verb|main.tex|. The file starts with 
% \verb|\documentclass{woosterthesis}|, which must be at the beginning of every IS. In the brackets are options for the woosterthesis class. The options are the same as for the \verb|book| class with some additional options 
% \verb|abstractonly|\index{woosterthesis options!abstractonly},
% \verb|acs|\index{woosterthesis options!acs},
% \verb|alltt|\index{woosterthesis options!alltt},
% \verb|apa|\index{woosterthesis options!apa},  
% \verb|blacklinks|\index{woosterthesis options!blacklinks},
% \verb|chicago|\index{woosterthesis options!chicago},
% \verb|citeorder|\index{woosterthesis options!citeorder},
% \verb|code|\index{woosterthesis options!code},
% \verb|colophon|\index{woosterthesis options!colophon},
% \verb|dropcaps|\index{woosterthesis options!dropcaps},
% \verb|euler|\index{woosterthesis options!euler},
% \verb|foreignlanguage|\index{woosterthesis options!foreignlanguage},
% \verb|guass|\index{woosterthesis options!guass}, 
% \verb|index|\index{woosterthesis options!index},
% \verb|kaukecopyright|\index{woosterthesis options!kaukecopyright},
% \verb|maple|\index{woosterthesis options!maple},
% \verb|minimalstyle|\index{woosterthesis options!minimalstyle},
% \verb|mla|\index{woosterthesis options!mla},
% \verb|nostyle|\index{woosterthesis options!nostyle},
% \verb|palatino|\index{woosterthesis options!palatino},
% \verb|picins|\index{woosterthesis options!picins},
% \verb|scottie|\index{woosterthesis options!scottie},
% \verb|singlespace|\index{woosterthesis options!singlespace},
% \verb|tikz|\index{woosterthesis options!tikz},
% \verb|verbatim|\index{woosterthesis options!verbatim},
% \verb|wblack|\index{woosterthesis options!wblack},
% and \verb|woostercopyright|\index{woosterthesis options!woostercopyright}. If no options are specified then the class default options \texttt{letterpaper}, \texttt{12pt}, \texttt{oneside} , \texttt{onecolumn} , \texttt{final}, and \texttt{openany} are used.

% The \verb|abstractonly| option will allow you to print just the Abstract. The \verb|acs| option implements the American Chemical Society citation and reference style. The \verb|alltt| option loads the \ip{alltt} package for using typewriter type in various ways and the \verb|apa| option implements the APA citation and reference style. The \verb|blacklinks| option will make the hyperlinks in the PDF version of the thesis black and suitable for printing; normally the links are colored to provide visual clues to the reader. The \verb|chicago| option implements Chicago style citation and references. The \verb|citeorder| option orders the references according to the citation order of the IS. The \verb|code| option will use \ip{listings} style to format program code examples. The \verb|colophon| option will include a colophon which is a section that describes the fonts and other settings used to produce the manuscript. \verb|dropcaps| loads the \ip{lettrine} package for doing dropped capitals and the \verb|euler| and \verb|guass| options load the \ip{woofncychap} package with the named option which will change the look of chapter headings. The \verb|foreignlanguage| option will load the \ip{csquotes} package and either the \ip{polyglossia} or \ip{babel} package depending on if \xt is being used to allow the input and formatting of sections of text in a foreign language. The \verb|index| option will allow the \ip{makeidx} package to be loaded so that if you have index entries they will be added to an index (this reqires additional steps).  The \verb|kaukecopyright| option will put the Kauke Hall symbol with the pre 2021 wordmark on the copyright page.  The \verb|maple| option will load the Maple package for including Maple code. The \verb|minimalstyle| option will use custom styling for the Table of Contents and List of Figures, Tables, and Listings and otherwise revert to the default \verb|book| class styles. The \verb|mla| option implements the MLA citation and reference style. The \verb|nostyle| option will remove all custom styling and revert to the default \verb|book| class styles. The \verb|palatino| option will use the \ip{pxfonts} package which uses the Palatino fonts. The \verb|picins| option will use the \ip{wrapfig} package to allow text to wrap around images and \verb|verbatim| allows one to set verbatim what is entered. The \verb|tikz| option loads the \ip{Ti\emph{k}Z} package enabling users to draw figures in their \lt document. The \verb|singlespace| option will use the \ip{setspace} package to typeset the document in singlespace. The \verb|wblack| option includes an opaque Wooster "W" (as of 8/2021) in the background of the title page instead of the default opaque Kauke Hall image, the \verb|scottie| option includes an opaque grayscale image of the Scottie mascot in the background of the title page instead of the default opaque Kauke Hall image, and the \verb|woostercopyright| option includes a copyright notice with the new (as of 8/2021) Wooster wordmark (see Appendix \ref{options} for images of what these options produce). Adding or deleting options from the comma separated list will change the appearance of the document and some options should only be used after consulting your advisor. Now let's move on to some other things that you'll need to deal with: text, figures, pictures, and tables.