\section{Testing Results}
To ensure the reliability and correctness of the system, both unit testing 
and integration testing were conducted across the core modules.

\textbf{Unit Testing}

Unit tests were conducted for all primary service components, including 
CuisineService, LocationService, and ReviewService. 
These tests aimed to validate the correctness of individual methods, 
the handling of sample inputs and the proper 
interaction with supporting components such as the cache layer and repositories.

Unit testing of the CuisineService class evaluated its core business logic and caching behavior.
Tests verified that when cuisine data was already present in the cache 
(cache hit), the service returned the correct data without querying the repository, 
ensuring optimal performance. When the cache did not contain the requested data 
(cache miss), the service correctly retrieved the data from the repository and 
stored it in the cache for future use. 

Unit tests also covered multiple retrieval methods, including fetching cuisines 
by region, by cuisine name, and by country. The tests validated 
that appropriate exceptions were thrown when a requested cuisine did not exist, 
demonstrating robust error handling.
Unit tests were also conducted for the LocationService and ReviewService modules,
covering typical data retrieval and error handling scenarios.
These tests followed the same methodology, confirming that all core services function correctly in isolation.

The successful execution of all unit tests confirms that each service correctly 
implements its core logic, manages entity relationships effectively, interacts 
properly with the cache and repository layers, and handles error scenarios gracefully. 
These results indicate that the system's business logic is reliable and functions 
as intended in isolation from the broader application.

\textbf{Integration Testing}

Integration testing was performed to validate the interactions between system modules 
and to ensure that end-to-end workflows function as intended. Each API endpoint was 
tested to confirm that requests from the frontend produced correct responses from the backend.

The tested workflows included retrieving cuisines for a selected region, 
fetching detailed information and reviews for a specific cuisine, 
submitting new reviews, and searching for restaurants based on cuisine 
and user location. These tests verified that the service layers correctly 
processed requests, that the database queries returned accurate results, 
and that responses were properly structured for consumption by the frontend.

In particular, tests for the review module confirmed that users can successfully 
submit new reviews for a cuisine through the API. Upon submission, the system 
correctly stores the review in the database and returns a response containing 
the rating and comment, ensuring that the data is accurately recorded. 
Additional tests verified that, when no reviews exist for a cuisine, 
the system returns an empty list, demonstrating correct handling of 
initial state scenarios.

Overall, the integration testing results provide confidence that the system 
operates as a cohesive unit, supporting user workflows from region selection 
to cuisine exploration, review submission, and restaurant recommendation 
without errors or unexpected behavior.