% \section[Caching]{Caching}\label{sec:newsec}
\chapter{Caching}\label{chap:caching}

\section[What is Caching]{What is Caching}
Caching data means to store frequently accessed data in a location that is easy and fast to access (usually in RAM). 
The purpose of caching is to ultimately increase the performance and efficiency when retrieving data. 
Data in a database is usually stored on a disk, which could be a hard drive or an SSD, which takes more time to process I/O. 
Caching could help decrease the amount of time to process this data significantly. It may then be questioned why all data is not simply stored in the cache, 
but this would be inefficient since the cache could not store a lot of data as much as the database does. The cost of the hardware of the cache is also significantly more expensive, 
and as the size of the cache increases, the search time will also increase, decreasing the speed and defeating the whole purpose of caching. 
Caching can be used at several levels. This article will mainly focus on caching in databases and web pages. 
There are multiple strategies that could be used when caching these two areas, but an important part of caching is the invalidation strategies. 
Deciding when the cache expires and when it updates could affect the performance and data consistency. Choosing the right technique in the given situation will be essential.

\input{chapters/theory/caching/dbStrategies}

\input{chapters/theory/caching/clientside}

\input{chapters/theory/caching/invalidation}